---
title: "AIC and Model Averaging"
output: ioslides_presentation
widescreen: true
smaller: true
---

## AIC and model averaging
Load following packages

```{r, warning=FALSE, error=FALSE, message = FALSE}
require(lme4)
require(MuMIn)
require(arm)
require(dplyr)
require(purrr)
require(broom)
```

## npk dataset
plant yield following manipulations of N, P, and K in 6 treatment blocks.
```{r,error=FALSE}
head(npk)
# attach(npk)
npk
```

## AIC in base R
Compare global to reduced model
```{r,error=FALSE}
# Global model (all additive terms)
global.lm <- lm(yield ~ N + K + P, data = npk)
# Make a reduced model
reduced.lm <- lm(yield ~ N + K, data = npk)
# Use AIC to compare with the global
AIC(global.lm, reduced.lm)
```

## Model Selection with MuMIn
Global mixed effects model with all possible interaction terms using lme4
```{r,error=FALSE}
global <-lmer(yield ~ N*P*K + (1|block),na.action = "na.fail", data = npk)
```

## Ranking models with AIC 
using dredge function
```{r, warning=FALSE,error=FALSE}
all.models <- dredge(global, rank ="AICc", m.lim=c(0,3), REML = FALSE)
all.models
```

## Model averaged parameter estimates
```{r,error=FALSE}
model.avg(all.models)
```

## Averaging across subsets
```{r,error=FALSE}
summary(model.avg(all.models, subset = delta < 4))
summary(model.avg(all.models, subset = cumsum(weight) <= .95)) ## or all models in the 95% CI
```

## Model averaged 95% CIs
The command *full = TRUE* gives full averages
```{r,error=FALSE}
confint(model.avg(all.models), level = 0.95)

```

## Standardizing Predictors
```{r, warning=FALSE,error=FALSE}
global.std <- standardize(global, standardize.y = FALSE, binary.input = "center")
all.models.std <- dredge(global.std, m.lim=c(0,3), REML = FALSE)
top.list <- get.models(all.models.std, subset = delta < 4)
```

## Table with AIC ranks and marginal and conditional R^2
```{r,error=FALSE}
top.sum <- summary(model.avg(all.models.std, subset = delta < 4))
model.out <- cbind(t(as.data.frame(lapply(top.list, FUN=r.squaredGLMM))),top.sum$msTable)
model.out
```

## Or using this function by Joey
```{r,error=FALSE}
# model.output <- top.list %>% 
#         map(r.squaredGLMM) %>%
#         as.data.frame(.)%>%
#         t(.) %>% 
#         as.data.frame(.) %>% 
#         bind_cols(., as.data.frame(summary(model.avg(all.models.std, subset = delta <
# 4))$msTable))
```
```{r}
r2 <- top.list %>% 
	map(r.squaredGLMM) %>% 
	map(t) %>% 
	map_df(as.data.frame, .id = "model")

aic.table <- all.models.std %>% 
	model.avg(subset = delta < 4) %>% 
	summary %>% 
	.$"msTable" %>% 
	add_rownames(var = "component_terms")

model.table <- bind_cols(r2, aic.table)
```

## Model output table
```{r}
model.table
```


## AIC output table
```{r,error=FALSE}
model.out
## or
model.table
```

## Model averaged slope and 95 CI table
```{r,error=FALSE}
top.sum <- summary(model.avg(all.models.std, subset = delta < 4))
est.ci <- cbind(top.sum$coefmat.subset,confint(top.sum))
est.ci
```

## To dredge or not to dredge?
```{r}
## set up a set of candidate models
mod1 <- lm(yield ~ N + K + P, data = npk) ## hyp: yeild varies as function of all three nutrients
mod2 <- lm(yield ~ N + K, data = npk) ## hyp: yield varies as a function of N and K
mod3 <- lm(yield ~ N, data = npk) ## hyp: yeild varies as a function of N only
mod4 <- lm(yield ~ N*P*K, data = npk) ## 

model.selection <- model.sel(mod1, mod2, mod3, mod4)
model.avg(model.selection, subset = delta <= 2)
## and then carry on with analysis as above
```

